---
title: "Entity Extraction Performance Evaluation - R & Python"
author: "Evan Canfield"
date: "12/30/2020"
output:
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
The purpose of this notebook is to test how to implement the Entity Extraction model to convert hypotheses into entities.

# Import
## Libraries
```{r import_libraries, message=FALSE}
  if (!require(pacman)) {install.packages('pacman')}
  p_load(
    dplyr,
    # purrr,
    quanteda,
    stringr,
    tidyr,
    tidytext
  )
```

## Source Files
The following imports functions defined in the sourced R scripts.
```{r load_source_files, warning=FALSE, message=FALSE}
# Import All Scripts
script_path <- "../R/"
file_paths <- list.files(recursive = TRUE, 
                         path = script_path, pattern = ".R", 
                         full.names = TRUE)

for (file in file_paths){
  source(file)
}
```

## Data
```{r import_data}
# PDF Input
## Define Path
folder_path <- "./../data/acadmic_papers_pdf_sample/"
pdf_paths <- list.files(recursive = FALSE, 
                       path = folder_path, 
                       pattern = ".pdf", 
                       full.names = TRUE)
```

## Python Modules
```{r}
np <- import("numpy")
joblib <- import("joblib")
nltk_stem <- import("nltk.stem")
```

## Causality Classification Model
```{r}
path_model <- "./../models/causality_bow_pipeline_naive_bayes.pkl"
model_causality <- joblib$load(path_model)
```
# Pre-process Steps
Before Causality Classification occurs, the following steps happen:

* Text Pre-processing
* Hypothesis Classification
* Entity Extraction

```{r}
# Text Pre-processing
pdf_path <- pdf_paths[8]
pdf_path
text_processed <- process_text(pdf_path)

# Hypothesis Classification
hypothesis <- hypothesis_extraction(text_processed, fasttext_tag = FALSE)

hypothesis_causality <- hypothesis %>% select(hypothesis_causality)

# Entity Extraction
entities <- entity_extraction(hypothesis)

entities
hypothesis_causality
```

# Processing

* remove punctuation
* replace node_1 / node_2

```{r}
pattern_punct <- "[[:punct:]]"

causality_01 <- hypothesis_causality %>% 
  bind_cols(entities) %>% 
  mutate(
    row_id= row_number()
  ) %>% 
  select(row_id, everything()) %>% 
  drop_na()  %>% 
  # modify_if(is.factor, as.character) %>% 
  mutate(
    hypothesis_causality = str_remove_all(hypothesis_causality, pattern_punct),
    cause = str_remove_all(cause, pattern_punct),
    effect = str_remove_all(effect, pattern_punct)
  ) %>% 
  mutate(
    causal_statement = str_replace(hypothesis_causality, cause, "node1"),
    causal_statement = str_replace(causal_statement, effect, "node2")
  )

causality_01
```
* Remove Stopwords
```{r}

causality_02 <- causality_01 %>% 
  unnest_tokens(word, causal_statement) %>% 
  anti_join(get_stopwords(), by = "word") %>% 
  select(row_id, word)

causality_02
```
* Lemmanize

```{r}
lemmatizer <- nltk_stem$WordNetLemmatizer()

causality_02

tokens <- causality_02 %>% pull(word)
 
tokens_lemm = vector(mode = "character", length = length(tokens))
for (i in seq_along(tokens)) {
  token = tokens[i]
  token_lemm <- lemmatizer$lemmatize(token)
  tokens_lemm[i] = token_lemm
}



causality_03 <- causality_02 %>% 
  bind_cols(tokens_lemm) %>% 
  rename(word_lemm = "...3") %>% 
  group_by(row_id) %>% 
  mutate(sentence = str_c(word_lemm, collapse = " ")) %>%
  select(-word, -word_lemm) %>% 
  distinct() %>% 
  pull(sentence)


```

# Model
## Dummy Data
```{r}
input <- c()
a <- "hypo node1 has a positive relationship on node2"
b <- "node1 behaves positively to node2"
c <- "node1 relationship on node2"
d <- "hypo node1 node2"
e <- "hypo 1 node1 likely use node2"
f <- "hypo 1 predicted increased use node1 would result increased node2 decreasedvoluntaryemployeeturnover"
g <- "hypo 3 positive effect node1 node2"
h <- "hypo 3 positive effect node1 node2"
input <- c(input, a, b, c, d, e, f, g, h)

model_causality$predict_proba(input)
```

## Actual Data
```{r}
causality_04 <- np_array(causality_03)

causality_pred <- model_causality$predict(causality_04)

causality <- data.frame(causality_pred) %>% rename(causality = causality_pred)

causality
```

# Function Test
```{r}
causality_output <- causality_classification(hypothesis)
```

