---
title: "Complete Process Performance Walkthrough"
author: "Evan Canfield"
date: "12/30/2020"
output:
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
The purpose of this notebook is to test how to implement the complete Causality Extraction NLP project.

# Import
## Libraries
```{r import_libraries, message=FALSE}
  if (!require(pacman)) {install.packages('pacman')}
  p_load(
    dplyr,
    purrr,
    quanteda,
    stringr,
    tidyr,
    tidytext
  )
```

## Source Files
The following imports functions defined in the sourced R scripts.
```{r load_source_files, warning=FALSE, message=FALSE}
# Import All Scripts
script_path <- "../R/"
file_paths <- list.files(recursive = TRUE, 
                         path = script_path, pattern = ".R", 
                         full.names = TRUE)

for (file in file_paths){
  source(file)
}
```

## Python Modules
```{r}
np <- import("numpy")
joblib <- import("joblib")
nltk_stem <- import("nltk.stem")
```


## Data
```{r import_data}
folder_path <- "./../data/acadmic_papers_pdf_sample/"
pdf_paths <- list.files(recursive = FALSE, 
                       path = folder_path, 
                       pattern = ".pdf", 
                       full.names = TRUE)
print(pdf_paths)
```
# Steps

* Text Pre-processing
* Hypothesis Extraction
* Entity Extraction
* Causality Classification
* Final Output Table


## Step By Step
```{r step_by_step, eval=FALSE}
m <- 1
n <- 10
input_paths <- pdf_paths[m:n]

i <- 1
lst_output <- vector(mode = "list", length = length(pdf_paths))

for (pdf in input_paths){

  file_name <- last(str_split(pdf, pattern = "/")[[1]])
  print(paste0("File Name: ", file_name))
  
  
  # Error Catching for PDF Conversion
  possible_error <- tryCatch({
      
      text_processed <- process_text(pdf)
      
    },
      
      error = function(e) { 
        e
        error_statement <- paste0("Error. File ", 
                                  file_name, 
                                  " could not be converted into text.")
        print(error_statement)
        
        }
      )
  
  ### Skip processing if error observed.
  if(inherits(possible_error, "error")) next 

  ## Extract Hypothesis
  hypothesis <- hypothesis_extraction(text_processed, fasttext_tag = FALSE)
  
  ### Test if Empty
  empty_hypothesis_test <- hypothesis %>% pull(hypothesis)
  hypothesis_empty <- is_empty(empty_hypothesis_test)
  

  if (!(hypothesis_empty)) {
    
    ## Entity Extraction
    entities <- entity_extraction(hypothesis)
    
    ### Test if Empty
    empty_entity_test <- entities %>% drop_na() %>% pull(cause)
    entity_empty <- is_empty(empty_entity_test)
    print(paste0("Entity Empty Test: ", entity_empty))

    
    if (!(entity_empty)) {
      
      ## Causality Classification
      causality_class <- causality_classification(hypothesis)
      causality_class <- data.frame(causality_class)
      
      # Compile Table
      iter_df <- cbind(hypothesis, entities) %>% drop_na()
      iter_df <- cbind(iter_df, causality_class)
      iter_df$file_name <- file_name
      
      # Modify Headers and Format
      iter_df <- iter_df %>% 
        rename(
          hypothesis_num = h_id,
          causal_relationship = causality_pred
        ) %>% 
        select(
          file_name, hypothesis_num, hypothesis, cause, 
          effect, causal_relationship
        ) %>% 
        modify_if(is.factor, as.character)
      
        lst_output[[i]] <- iter_df
        i <- i + 1
    } else {
      
      print(paste0("Entity Not Detected: ", file_name)
            
    } 
  } else { 
    
    print(paste0("Hypothesis Not Extracted: ", file_name)
          
  }
}

lst_output <- lst_output[lengths(lst_output) != 0]
```

# Test Function
## Single PDF
```{r function_file_single, eval  = FALSE}
m <- 1
n <- 3
input_paths <- pdf_paths[n]

gen_output_table(file_path = input_paths)
```

# List of Multiple PDFs
```{r function_file_multiple, eval  = FALSE}
m <- 1
n <- 3
input_paths <- pdf_paths[m:n]
gen_output_table(file_path = input_paths)
```

# Folder
```{r function_folder}
folder_path <- "./../data/acadmic_papers_pdf/"

gen_output_table(folder_path = folder_path)
```

