---
title: "Entity Extraction Performance Evaluation - R & Python"
author: "Evan Canfield"
date: "12/30/2020"
output:
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
The purpose of this notebook is to test how to implement the Entity Extraction model to convert hypotheses into entities.

# Import
## Libraries
```{r import_libraries, message=FALSE}
  if (!require(pacman)) {install.packages('pacman')}
  p_load(
    dplyr,
    purrr,
    stringr,
    tidyr
  )
```

## Source Files
The following imports functions defined in the sourced R scripts.
```{r load_source_files, warning=FALSE, message=FALSE}
# Import All Scripts
script_path <- "../R/"
file_paths <- list.files(recursive = TRUE, 
                         path = script_path, pattern = ".R", 
                         full.names = TRUE)

for (file in file_paths){
  source(file)
}
```

## Data
```{r import_data}
# PDF Input
## Define Path
pdf_path <- "./../data/acadmic_papers_pdf_sample/jv04amj.pdf"
```

## Python Modules


# Pre-process Steps
Before Causality Classification occurs, the following steps happen:

* Text Pre-processing
* Hypothesis Classification
* Entity Extraction


```{r}
# Text Pre-processing
text_raw <- pdf_to_text(pdf_path)
text_processed <- process_text(input_text = text_raw)

# Hypothesis Classification
hypothesis <- extract_hypothesis(text_processed)
hypothesis_vec <- hypothesis %>% pull(hypothesis)
hypothesis

# Entity Extraction
entities <- entity_extraction_mult(hypothesis_vec)
entities
```

# Replace Entity With Node
```{r}

pattern_punct <- "[[:punct:]]"

causality <- hypothesis %>% 
  bind_cols(entities) %>% 
  mutate(
    row_id= row_number()
  ) %>% 
  select(row_id, everything()) %>% 
  drop_na()%>% 
  modify_if(is.factor, as.character) %>% 
  mutate(
    hypothesis = str_remove_all(hypothesis, pattern_punct),
    cause = str_remove_all(cause, pattern_punct),
    effect = str_remove_all(effect, pattern_punct)
  ) %>% 
  mutate(
    causal_statement = str_replace(hypothesis, cause, "node_1"),
    causal_statement = str_replace(causal_statement, effect, "node_2")
  )

causality
```


## Process Text and Extract Hypotheses
First, we process our raw input and extract hypotheses.
```{r process_extract_hypothesis}
# Process Text
text_processed <- process_text(input_text = pdf_txt_raw)

# Extract Hypothesis
hypo_xtr_vec <- extract_hypothesis(text_processed) %>% 
  select(hypothesis) %>% 
  pull()
```

# Hypothesis Selection
For the following process, one hypothesis will be selected as a indicative sample. We will use this hypothesis to work through the process of turning a hypothesis into two extracted entities. Once the process is solidified, we can apply it across all available hypothesis.
```{r select_exmample_hypothesis}
n = 1
hypothesis <- hypo_xtr_vec[n]
hypothesis
```

## Generate Predictions
We now generate predicted Entity class for the hypothesis. The model return a 1D array for each input hypothesis, so we must convert the 1D array to a vector.

```{r generate_classes}
pred_classes <- gen_entity_class(hypothesis)

pred_classes
```

# Extract Entities
With our example hypothesis selected, our first step is to generate a list of indexes fo where Node 1 and Node 2 were predicted.
```{r}
index_entities <- gen_entity_class_index(pred_classes)
```
With the indexes of each Node identified, some processing has to occur. Generally, the Node 1 and Node 2 indexes are grouped with the sample class, and distinct from each other. A sample seletion of the Entity Extraction model output might look like the following:

* 0, 0, 1, 1, 1, 0, 0, 2, 2, 2, 2, 0, 0, 0 

From the above model output, we can clearly see where the Node 1 and Node 2 entities are, and we can go forward and extract from from the hypothesis text. 

Unfortunately the model output is not always so clear. The following are possible issues that need to be addressed:

* Node 1 and Node 2 indexes overlap
 * 0, 0, 1, 1, 2, 1, 0, 0, 2, 2, 2, 0, 0, 0 
 
* Node 1 or Node 2 contain a predicted index that is far from the majority of the cases(outliers)
 * 0, 0, 1, 1, 1, 0, 0, 2, 2, 2, 2, 0, 0, 0, 0, 0, 0, 0, 0, 2
 
In order to extract distinct entities, we need to process any predictions experiencing the above issues.

## Overlap
For overlapping entities we define a function. When there is overlap, the function trims one of the overlapping indexes. This process repeats until there is no overlap. The Node which get's trimmed is the Node with the longest span. In the case of equal length nodes, Node 2 is trimmed.

With the function defined, we can execute on the sample hypothesis.
```{r}
print("Nodes Indexes - Pre")
print(index_entities)

# Verify Both Entities Detected
both_entity_present <- vector_is_empty(index_entities[[1]]) & 
  vector_is_empty(index_entities[[2]])

# Trim Overlap
if (both_entity_present) {
  index_entities <- trim_overlapping_entities(index_entities)
}


print("Nodes Indexes - Post")
print(index_entities)
```

## Outliers
For outlier predicted classes, we use the standard Box Plot outlier definition, *1.5 x Interquartile Range*. We define a function which identifies outlier indexes and the trims them.

```{r}
print("Nodes Indexes - Pre")
print(index_entities)
index_entities <- trim_outlier_indexes(index_entities)
print("Nodes Indexes - Post")
print(index_entities)
```
## Convert Index to Strings
With out entity nodes processed, we can now convert index lists to text strings.
The following function inputs the original hypothesis text, and outputs the extracted entities.
```{r}
paste0("Entity 1 - Index: ", index_entities[[1]])
paste0("Entity 2 - Index: ", index_entities[[2]])
str_entites <- index_to_entity(hypothesis, index_entities)
str_entites

paste0("Entity 1 - Text: ", str_entites[1])
paste0("Entity 2 - Text: ", str_entites[2])
```

# Wrapper Functions
## Individual Hypothesis
The following code block executes the complete Entity Extraction process for a individual hypothesis.

```{r}
wrapper_test_indv <- wrapper_entity_extraction_indv(hypothesis)
wrapper_test_indv
```

## Multiple Hypotheses
The followings tests the Entity Extraction process on a list of extracted hypotheses.
```{r}
wrapper_test_mult <- wrapper_entity_extraction_mult(hypo_xtr_vec)
wrapper_test_mult
```


